---
title: "Assignment 3"
author: "Fabrizio Fiorini"
date: "10/9/2021"
output: html_document
---

# Post-Optimality and Sensitivity Analysis

## Loading the necessary libraries

```{r}
setwd("C:/Users/Fabrizio/Desktop/MyBlackBoard/MIS 64018 - Quant. Management Modeling/Module 5 - Post Optimality Analysis and Duality Theory/Assignment 3")
library(lpSolveAPI)
```

## Introduction



## Solve the LP Model

In this assignment, we chose to write the problem formulation in the lp format, a text file created specifically for this problem, that includes all the information. 

```{r}
x <- read.lp("Weigelt_Corporation_Assignment3.lp")
x
```

Now that the file has been read by R, we can solve it.

```{r}
solve(x)
```

Here, zero means that R found an optimal solution.

```{r}
get.objective(x)
get.variables(x)
```

From the results we can understand what is the optimal production mix among the 3 product sizes and the 3 plants in order to obtain the maximum profit.
According to the model solution:
- in Plant 1 the company should produce 517 Large size and 178 Medium size.
- in Plant 2 it should produce 667 Medium size and 167 Small size.
- in Plant 3 it should produce exclusively 417 Small size.
With this production levels the company would register an expected profit of $696,000.

```{r}
get.constraints(x)
```

These are the RHS values for our 11 constraints.

## Post-Optimality and Sensitivity Analysis

```{r}
get.sensitivity.rhs(x) #shadow prices
get.sensitivity.obj(x) #reduced costs
```

According to the output, the shadow prices of our constraints   



## Solve the Dual LP Model

```{r}
y <- read.lp("Weigelt_Corporation_Dual_Assignment3.lp")
y
```

```{r}
#set boundaries for columns 10 and 11, default for the rest
set.bounds(y, lower = c(-Inf, -Inf), columns = 10:11) 
```

Now that the file has been read by R and we set the boundary, we can solve it.

```{r}
solve(y)
```

Here, zero means that R found an optimal solution.

```{r}
get.objective(y)
get.variables(y)
```

These are the RHS values for our 11 constraints.

## Post-Optimality and Sensitivity Analysis

```{r}
get.sensitivity.rhs(y) #shadow prices
get.sensitivity.obj(y) #reduced costs
```


